\chapter{System overview}

\eyebrow{how the pieces fit}

\vspace{4pt}
CARCASS is a single native desktop application. A Go core owns the window, the
database and the business logic; a React front end draws the interface inside the
operating system's native WebView; and Python \emph{sidecars} run the parts that
need PyTorch or OpenCV --- model inference, real-time overlay, and conformation.

\section{Architecture}

\begin{center}
\begin{tcolorbox}[colback=codebg,colframe=hair,boxrule=0.6pt,arc=3pt,width=\linewidth]
\ttfamily\small
Single native binary (Wails)\\
\hspace*{1em}|\\
\hspace*{1em}+-- React front end \ (dark instrument UI, drawn by the WebView)\\
\hspace*{1em}|\hspace*{4em}$\updownarrow$ typed Go$\leftrightarrow$JS bridge\\
\hspace*{1em}+-- Go core\\
\hspace*{2em}\ \ \ +-- store \ \ (single SQLite file: the "one spreadsheet")\\
\hspace*{2em}\ \ \ +-- images/ \ (paired image folders on disk)\\
\hspace*{2em}\ \ \ +-- Python sidecars (spawned as needed):\\
\hspace*{4em}\ \ \ +-- inference.py \ \ (fat segmentation, grade, cutout)\\
\hspace*{4em}\ \ \ +-- realtime.py \ \ \ (live fat overlay, background subtraction)\\
\hspace*{4em}\ \ \ +-- conformation.py (integral convexity, analytical)\\
\hspace*{4em}\ \ \ +-- kinect\_capture.py (optional RGB+depth)
\end{tcolorbox}
\end{center}

\subsection*{Three principles}

\begin{enumerate}[leftmargin=1.4em,itemsep=4pt]
  \item \textbf{The database is the source of truth for pairing.} An image never
        carries its link in its filename. The flow is always: select or create
        the carcass, then capture/import \emph{inside} that carcass's context, so
        the image is written with its \tele{carcass\_id} already set.
        Reconstruction by file order is structurally impossible.
  \item \textbf{Capture sources are interchangeable.} Webcam capture runs in the
        front end via the browser camera API; the Kinect (depth) runs through a
        Python sidecar; both are just sources of a paired image.
  \item \textbf{Measurements come with honesty about their status.} Colour
        encodes state: \pillok{validated} (green) for fat segmentation,
        \pillalert{experimental} (amber) for the grades, and red reserved for
        broken pairing --- never for a data series.
\end{enumerate}

\section{Technology stack}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l l X@{}}
\toprule
\textbf{Layer} & \textbf{Technology} & \textbf{Role} \\
\midrule
Desktop shell & Wails v2 (Go) & Window, embed front end, Go$\leftrightarrow$JS bridge \\
Core          & Go 1.23+      & Database, pairing, orchestration \\
Database      & SQLite (pure-Go) & Single \tele{carcass.db} --- the one spreadsheet \\
Front end     & React 19 + Vite + TypeScript & The instrument interface \\
Styling       & Tailwind 4, shadcn/ui & Open MCT "Espresso" theme \\
Inference     & Python + PyTorch & Fat / grade / conformation models \\
Vision        & OpenCV, scikit-image, rembg & Cutout, convexity, background removal \\
\bottomrule
\end{tabularx}
\end{center}

\section{Where data lives}

Everything is stored locally, under the operating system's application-data
directory:

\begin{lstlisting}
<app data>/carcass-integration/
|-- carcass.db          # the single database: batches, carcasses,
|                       #   images, raters, grades, analyses
`-- images/
    `-- batch_<id>/
        `-- carcass_<tag>/
            |-- rgb_<uuid>.jpg        # the paired image
            `-- analysis/             # model outputs (masks, overlays,
                                      #   convexity maps)
\end{lstlisting}

\begin{note}[title=The single database is the "one spreadsheet"]
The original research requirement was a single spreadsheet, filled in at
collection time, that records the image--animal link. Here that spreadsheet is
\tele{carcass.db}: one file, one source of truth, portable and auditable.
\end{note}
