\chapter{The interface}

\eyebrow{reading the interface}

\vspace{4pt}
Apex follows the layout conventions of mission-control software. The window is
organised into fixed regions. Operation proceeds by \textbf{selecting an object}
in the navigation tree and \textbf{choosing a view} of it.

\section{Anatomy of the window}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\toprule
\textbf{Region} & \textbf{What it holds} \\
\midrule
Title bar (top) & Product mark and a live readout: carcasses, images, graded. \\
Navigation tree (left) & Root objects (Live monitor, Import images, Project dashboard) and the data hierarchy \textbf{Batches\,$\rightarrow$\,Carcasses}. \\
Browse bar (above centre) & The path (breadcrumb) of the selected object, and a \textbf{view switcher} on the right. \\
Main area (centre) & The selected object's active view. \\
Inspector (right) & Read-only properties of the selected object. Collapsible. \\
Status bar (bottom) & Engine state, device, and dataset counts. \\
\bottomrule
\end{tabularx}
\end{center}

\section{Objects and views}

Selecting an object in the tree changes both the breadcrumb and the set of views
available in the browse bar:

\begin{center}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\toprule
\textbf{Object} & \textbf{Views (in the browse bar)} \\
\midrule
A \textbf{batch}   & Overview, Analysis, Grading \\
A \textbf{carcass} & Overview, Images, Analysis \\
Live monitor       & Live monitor \\
Import images      & Import \\
Project dashboard  & Dashboard \\
\bottomrule
\end{tabularx}
\end{center}

\begin{note}[title=The Inspector tracks the current selection]
For the selected object (a batch or a carcass), the right-hand Inspector shows
its properties: for a carcass, its identification, physical reference and model
analysis; for a batch, its counts and fat statistics. It is read-only; editing
occurs in the views.
\end{note}

The status bar at the bottom reports engine state: whether the inference
\tele{engine} is \pillok{ready} and on which \tele{device} (e.g. \tele{mps}),
together with the running dataset totals.
