\chapter{Inter-rater grading}

\eyebrow{independent, blind scores + agreement}

\vspace{4pt}
The \textbf{Grading} view of a batch collects grades from multiple assessors, each
scoring independently and blind, and measures how much they agree. This is the
human reference the research requires --- a grade assigned \emph{over the image},
with a measure of its reliability.

\section{How a session works}

\begin{enumerate}[leftmargin=1.4em,itemsep=3pt]
  \item Add or choose a \textbf{rater}.
  \item Start a \textbf{blind session} on the batch --- other raters' scores are
        hidden, so each assessment is independent.
  \item For each carcass with an image, score two axes on a 1--5 scale:
        \textbf{Conformation} (shape and muscle development, observable in the
        image) and \textbf{Finishing} (fat cover).
\end{enumerate}

\section{Agreement}

Once at least two raters have scored the same set of carcasses, the Project
dashboard reports the inter-rater agreement with \textbf{Fleiss' $\kappa$} per
axis, together with a consensus grade. If agreement is insufficient the consensus
is flagged --- exactly the guard-rail the research needs before trusting a grade
as reference.

\begin{note}[title={Two axes, two different confidences}]
\emph{Conformation} is observable in the image. \emph{Finishing} depends on fat
cover, a depth property that a single surface projection captures only partly ---
the interface notes this, and full predictive validation of finishing depends on
the physical reference measured on the same animals.
\end{note}
