\chapter{Scientific scope and limitations}

\eyebrow{what the numbers can and cannot claim}

\vspace{4pt}
Apex is built to be honest about the boundary between what its measurements
establish and what remains open. This chapter states that boundary explicitly.

\section{What is validated}

\begin{itemize}[leftmargin=1.3em,itemsep=3pt]
  \item \textbf{Fat segmentation} is validated (IoU $\sim$0.92) and reliable, once
        the background has been removed so the model sees the conditions it was
        trained on.
  \item \textbf{Verifiable pairing} is guaranteed by construction: every image
        carries its \tele{carcass\_id} from the moment of capture or import.
  \item \textbf{Conformation convexity} is an objective, reproducible measurement
        of the profile, invariant to pose and lighting; its correspondence to
        anatomy is verifiable by eye.
\end{itemize}

\section{What is not validated}

The two \emph{grades} (finishing and conformation) are estimates, not
settled predictions. This is grounded in the project's oracle experiment, which
tested whether conformation is recoverable from a single 2D image:

\begin{caution}[title=The oracle result]
Computing shape descriptors on the \emph{perfect manual annotation} (the best
mask any model could produce), \textbf{zero of 384 statistical tests survived
multiple-comparison correction} at n=22. Even with perfect segmentation,
conformation is not reliably recoverable from a single 2D image at this sample
size. The bottleneck is the acquisition modality, not the model.
\end{caution}

Therefore the software presents these grades as \pillalert{estimates}, never as
facts, and marks them in amber wherever they appear.

\section{Why this matters, and how it is resolved}

The validation the grades lack requires exactly one thing: grades correctly
paired to images, on a larger sample. That is precisely what Apex is built to
collect. As the paired dataset grows, the \textbf{Physical correlation} tab
(Station~7) can test whether the surface measurements predict the physical
reference and the assessor grades. This closes the loop that the earlier research
could not.

\section{Modality caveats}

\begin{itemize}[leftmargin=1.3em,itemsep=3pt]
  \item \textbf{Fat cover (finishing)} is a depth property; a single surface
        image captures it only partly. Depth capture (Kinect) is supported in the
        schema for future work.
  \item \textbf{Standardised capture} matters: a fixed background, uniform
        lighting and a consistent view improve every downstream measurement. The
        software imposes a required view and offers background capture, but the
        physical setup is the operator's responsibility.
  \item \textbf{Sample size.} The current models come from n=22. Their estimates
        should be read as exploratory until the target sample is collected and
        the validation loop is run.
\end{itemize}

\begin{note}[title=The through-line]
The earlier study did not fail at its methods. It failed at data integrity.
Apex exists to fix that first. Every honest limitation above is a reason the
software is built the way it is: collect a trustworthy, paired dataset, and let
validation follow.
\end{note}
